---
title: "Plot simulation summary data"
author: "Elena Tartaglia"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    df_print: paged
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(boot) # for inv.logit function
library(RColorBrewer) # for colour schemes in plots
# library(scales) this library is used for making percentage scales
source(here::here("simulation_study",
                  "simulation_stan_analysis",
                  "combine_simulated_data.R"))
```


```{r}
summary_data = summary_data %>%
  mutate(
    num_total_rows = num_line_rows + num_container_rows,
    percentage_container_data = num_container_rows/num_total_rows
    )
```



# Standard deviation of parameters



```{r}
df = summary_data %>%
  filter(num_total_rows == 1000,
         min_entry_size == 2,
         max_entry_size == 5,
         entry_correlation_sd == 0,
         !(param_name %in% c("lp__", "entry_effect[1]"))) 

ggplot(df, aes(x = percentage_container_data, y = summary_sd)) +
  geom_line() +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1)) +
  facet_wrap(~param_name, scales = "free") +
  labs(title = "Standard deviation of parameter estimates by percentage container data",
       subtitle = paste("Min entry size:", first(df$min_entry_size),
                        "Max entry size:", first(df$max_entry_size),
                        "Entry correlation:", first(df$entry_correlation_sd)))
```



```{r, fig.width=16, fig.height=14}
df = summary_data %>%
  filter(min_entry_size == max_entry_size, !(param_name %in% c("lp__", "entry_effect[1]", "sigma_entry")), num_total_rows >= 1000)

df %>%
  select(min_entry_size, max_entry_size, percentage_container_data, num_total_rows) %>% 
  arrange(min_entry_size, max_entry_size, percentage_container_data, num_total_rows) %>%
  unique()


ggplot(df, aes(x = num_total_rows, y = summary_sd, color = as.factor(percentage_container_data))) +
  geom_point() +
  geom_line() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_grid(min_entry_size~param_name) + 
  scale_color_discrete(name = "Ratio container data") +
  labs("Standard deviation of parameter estimates by amount of data")
```



- Having a higher percentage of container data increases the standard deviation, but this matters less when entries are smaller.




# Prior

Draw from the prior and plot to see what it looks like.


```{r}
N = 1000000
set.seed(147)
pint = rnorm(N, -1, 2)
beta_doc = rnorm(N, 0, 0.5)
country_effect = rnorm(N, 0, 0.5)
sigma_entry = runif(N, 0, 0.5)
entry_effect = sapply(sigma_entry, function(sigma) rnorm(1, 0, sigma))
zeros = rep(0, N)

# 4 possible combinations: beta doc or not, entry effect or not.
prior_df = data.frame(
  pint = rep(pint, 4),
  country_effect = rep(country_effect, 4),
  beta_doc = rep(c(beta_doc, zeros), 2),
  entry_effect = c(rep(entry_effect, 2), rep(zeros, 2))
  ) %>%
  mutate(
    p = inv.logit(pint + country_effect + beta_doc + entry_effect)
  )
```


These plots assume probability of documentation is 1/2



```{r}
prior_df %>%
  filter(entry_effect > 0) %>%
ggplot(aes(x = p)) +
  geom_histogram(binwidth = 0.025) +
  labs(title = "Prior with entry effect")
```


```{r}
prior_df %>%
  filter(entry_effect == 0) %>%
ggplot(aes(x = p)) +
  geom_histogram(binwidth = 0.025) +
  labs(title = "Prior without entry effect")
```


# Check parameter estimates

Check parameter estimates against exact values from `simulate_data.R`.

*TODO: Check these with Chris*

```{r}
exact_df = data.frame(
  param_type = c(rep("p_intercept", 8), rep("country_effect", 3), "beta_doc"),
  param_name = c(paste0("p_intercept[", seq(8), "]"), paste0("country_effect[", seq(3), "]"), "beta_doc"),
  yintercept = c(qlogis(c(.01, .05, .1, .2, .5, .7, .9, .95)), .5, -1, .25, 0.2)
)
```




```{r, fig.width=10}
df = summary_data %>%
  filter(num_total_rows == 1000,
         min_entry_size == 2,
         max_entry_size == 5,
         entry_correlation_sd == 0,
         !(param_name %in% c("lp__", "entry_effect[1]", "sigma_entry"))) %>%
  mutate(
    param_type = case_when(
      gsub("[^a-zA-Z]", "", param_name) == "pintercept" ~ "p_intercept",
      gsub("[^a-zA-Z]", "", param_name) == "countryeffect" ~ "country_effect",
      TRUE ~ "beta_doc"
    )
  ) %>%
  relocate(param_name, param_type)

mycolors <- colorRampPalette(brewer.pal(8, "Dark2"))(nrow(exact_df))

ggplot(df, aes(x = percentage_container_data, y = summary_mean, color = param_name)) +
  geom_point() +
  geom_line(linetype = "dashed") +
  facet_wrap(.~param_type) +
  geom_hline(data = exact_df, aes(yintercept = yintercept, color = param_name)) + 
  scale_color_manual(values=mycolors) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1)) +
  labs(title = "Mean parameter estimates by percentage container data",
       subtitle = paste("Min entry size:", first(df$min_entry_size),
                        "Max entry size:", first(df$max_entry_size),
                        "Entry correlation:", first(df$entry_correlation_sd)))
  
```


- Beta doc doesn't seem to match it's exact value: do I have the correct exact value?

- Estimates for large (positive or negative) `p_intercept` are worse.

- Estimate for `p_intercept[5]` gets worse as the percentage of container data increases



```{r, fig.width=16, fig.height=14}
df = summary_data %>%
  filter(min_entry_size == max_entry_size, !(param_name %in% c("lp__", "entry_effect[1]", "sigma_entry")), num_total_rows >= 1000) %>%
  mutate(
    `Entry Size` = min_entry_size # have selected out data where min and max entry size are equal
  )


ggplot(df, aes(x = num_total_rows, y = summary_mean, color = as.factor(percentage_container_data))) +
  geom_point() +
  geom_line(linetype = "dashed") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_hline(data = exact_df, aes(yintercept = yintercept, linetype = "Exact")) + 
  facet_grid(`Entry Size`~param_name, labeller = labeller(.rows = label_both, .cols = label_value)) + 
  scale_color_discrete(name = "Ratio container data") +
  scale_linetype_manual(name = "Data type", values = 1) +
  labs("Mean parameter estiamtes by amount of data")

```


- Estimates get worse as the entry size increases (estimates get worse down the page)

- Estimates get worse as ratio of container data increases (blue estimates are worse than pink)

- Estimates tend to improve with increased data (estimates improve left to right), but sometimes they seem to stabilise away from the exact value.










